BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models

### 2024-08-01 paper.tex
Minor fixes

\textbf{Third}, we applied our tool to eight \textbf{realistic models}, where three models (e001, e002, e020) are taken from~\cite{houhouFirstOrderLogicVerification2022}, and the remaining five models are part of the Camunda BPMN for research repository\footnote{\url{https://github.com/camunda/bpmn-for-research} \label{footnote:camundaResearch}}.
\autoref{tab:realistic-models-benchmark} shows each model's average runtime and number of states.
The BPMN Analyzer takes 1-10ms for e001, e002, and e020~\cite{krauterInstantaneousComprehensibleFixable2024}, while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterHigherorderTransformationApproach2024} report 3.66-10.26s and 1-1.75s respectively.
The benchmarks in~\cite{krauterHigherorderTransformationApproach2024} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was less powerful.
In general, our analysis is instantaneous for nearly all models since most have less than 1000 states according to~\cite{fahlandAnalysisDemandInstantaneous2011}.

@@

% Counterexample
\textbf{Second}, we use \textit{tokens} to visualize errors \textit{interactively}, i.e., show an execution leading to the error.
Our analysis provides sample executions resulting in the found control-flow errors, which we visualize in the editor by showing how tokens move from the process start to an erroneous state.
We are unaware of other tools that visualize errors directly and allow for interactions, such as stopping/resuming and restarting.

>>>>

\textbf{Third}, we applied our tool to eight \textbf{realistic models}, where three models (e001, e002, e020) are taken from~\cite{houhouFirstOrderLogicVerification2022}, and the remaining five models are part of the Camunda BPMN for research repository\footnote{\url{https://github.com/camunda/bpmn-for-research} \label{footnote:camundaResearch}}.
\autoref{tab:realistic-models-benchmark} shows each model's average runtime and number of states.
The BPMN Analyzer takes 1-10ms for e001, e002, and e020~\cite{krauterInstantaneousComprehensibleFixable2024}, while~\cite{houhouFirstOrderLogicVerification2022} and~\cite{krauterHigherorderTransformationApproach2024} report 3.66-10.26s and 1-1.75s respectively.
The benchmarks in~\cite{krauterHigherorderTransformationApproach2024} were run on the same hardware, while the machine used in~\cite{houhouFirstOrderLogicVerification2022} was less powerful.
Our analysis is instantaneous for nearly all BPMN models since most have less than 1000 states, according to~\cite{fahlandAnalysisDemandInstantaneous2011}.

@@

% Counterexample
\textbf{Second}, we use \textit{tokens} to visualize errors \textit{interactively}, i.e., show an execution leading to the error.
Our analysis provides sample executions resulting in the found control-flow errors, which we visualize in the editor by showing how tokens move from the process start to an erroneous state.
We are unaware of other tools that visualize errors directly and allow interactions, such as stopping/resuming and restarting.
